LAGOS lake depth

### 2021-12-06 figures/00_maps.Rmd
towards figure panel labels, #16

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.5}
theme_opts <- guides(color = guide_legend(
  override.aes = list(size = 2)))
cowplot::plot_grid(gg_bathy + theme_opts,
  gg_shapeclass + theme_opts,
  gg_reservoir + theme_opts,
  ncol = 1)
```

>>>>

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.5}
theme_opts <- guides(color = guide_legend(
  override.aes = list(size = 2)))
cowplot::plot_grid(gg_bathy + theme_opts,
  gg_shapeclass + theme_opts,
  gg_reservoir + theme_opts,
  labels = c("a", "b", "c")
  ncol = 1)
```
